\documentclass[12pt]{article}

\usepackage[
    a4paper, headsep=1.5cm, headheight=30pt,
    left=2.5cm,right=2.5cm,top=4cm,bottom=3cm]{geometry}
\usepackage{fancyhdr}
\usepackage{enumitem}

\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{graphicx}
\usepackage[font=footnotesize]{caption}
\usepackage{float}
\graphicspath{ {./figures/} }


\begin{document}

\begin{titlepage}
       \vspace*{2cm}

       \LARGE
        GCfit

       \vspace{2cm}

       \Huge
       \textbf{Globular Cluster Observation Data}

       \vspace{2cm}
        
        \LARGE
        Data File Catalog

       \vspace{1.5cm}

       \vfill

       Version 2
       January 18, 2022
\end{titlepage}

\section{Introduction}

All datasets are stored in a `Hierarchical Data Format' (HDF5) file.

A data group\footnote{Contrary to HDF standards, in all project documentation a
`Dataset' does not refer to the typical HDF dataset, but is analogous to a
specific HDF group while `Variable's are most analogous to HDF datasets. In this
document, the standard HDF group/dataset notation will be used.} must contain
all data representing a single observational product, that is, all
datasets associated to a single physical process,
from a single source, along with all relevant metadata.

All data corresponding to a single data group should exist within the relevant
`key' group (given below) under the file root group, which corresponds to a
physical process or observable. If multiple groups exist covering the same
observation type (Ex: Multiple different sources observing proper motion
profiles) Then those groups must exist as further subgroups within the `key'
group (Ex: \texttt{/proper\_motion/sourceA/} and
\texttt{/proper\_motion/sourceB/}). However, all subgroups must exist within the
key at the same level. No unequal nesting or shared space is allowed.

Each group has a number of required datasets, which are detailed below. Each
dataset may have required supplementary datasets as well, such as uncertainties.
Each dataset may also require certain metadata fields, such as unit names, to
be stored as attributes on the dataset itself.

\section{Attributes}

Overall cluster attributes and metadata are stored as attributes to the
file root group. Certain attributes are required for fitting certain
observables. Some attributes, when required for model creation, are given
default values, if they do not exist in the file. All attributes stored must
correspond to the units given below as they will be assumed at runtime.

\begin{center}
\begin{table}[H]
\begin{tabular}{ | c | c | c | c | c | }
    \hline
    Variable & Attribute Name & Notes & Default Value & Units \\
    \hline\hline
    Galactic Longitude & \texttt{l} &
    Required for pulsar fitting & N/A & degrees \\
    \hline
    Galactic Latitude & \texttt{b}  &
    Required for pulsar fitting & N/A & degrees \\
    \hline
    Right Ascension & \texttt{RA} &
    Required for mass function fitting & N/A & degrees \\
    \hline
    Declination & \texttt{DEC}  &
    Required for mass function fitting & N/A & degrees \\
    \hline
    Metallicity [Fe/He] & \texttt{FeHe} &
    Defines mass function evolution & -1.00 & dex \\
    \hline
    Age & \texttt{age} & Defines mass function evolution & 12 & Gyr \\
    \hline
    Total Proper Motion & \texttt{\(\mu\)} &
    Required for pulsar fitting & N/A & mas/yr \\
    \hline
    Total escape rate \(\dot{N}\) & \texttt{Ndot} &
    Defines mass function evolution & 0 & \\
    \hline
\end{tabular}
\end{table}
\end{center}
% TODO document the sources of ^ somehow (and units as well), within the file

\newpage

\input{DP_initials}

\newpage
\section{Data Products}

* denotes required fields

\input{DP_pulsar.tex}

\input{DP_numberdensity.tex}

\input{DP_propermotion.tex}

\input{DP_velocitydispersion.tex}

\input{DP_massfunction.tex}


\end{document}

